### 2010-07-14 subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: manual updated (installation)

@@

The display server can present HTML forms and send data from a form to a client
when the form is submitted.

@@

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
#ifdef FEAT_VISUALIZATION
   class COrDisplayClient: public cogx::display::CDisplayClient
   {
      CObjectRecognizer* pRecognizer;
   public:
      void createForms();
      void handleForm(const std::string& id, const std::string& partId,
            const std::map<std::string, std::string>& fields); /*override*/
      bool getFormData(const std::string& id, const std::string& partId,
            std::map<std::string, std::string>& fields); /*override*/
   };
\end{Verbatim}

A form can be defined with standard HTML form elements but it must not be
enclosed in the \code{"<form>"} tag which is added by the Display Server.

>>>>

\subsection{Java client interface}

To build the Java client interface add the following to the main build.xml file:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   <target name="template" depends="init">
      ...
      <ant target="${target}" dir="subarchitectures/visualization.sa" />
      ...
   </target>
\end{Verbatim}

\subsection{Python client interface}

The Python client interface is installed as part of the CMake installation
process. To enable the installation the following steps should be performed:

\begin{enumerate}
   \item Add to \verb|svn:externals| of the CogX root directory:

   \begin{Verbatim}[fontsize=\scriptsize,gobble=6]
      ^/code/tools/python/trunk         tools/python
   \end{Verbatim}

   \item Perform an update get tools/python and cmake/PythonBuild.cmake:

   \begin{Verbatim}[fontsize=\scriptsize,gobble=6]
      svn update
   \end{Verbatim}

   \item Add at the beginning of the main CMakeLists.txt file, \\
   somewhere {\em after} {\scriptsize \verb|set(CMAKE_INSTALL_PREFIX ...)|}:

   \begin{Verbatim}[fontsize=\scriptsize,gobble=6]
      include(cmake/PythonBuild.cmake)
   \end{Verbatim}

   \item Check that the option \verb|BUILD_PYTHON_COMPONENTS| is ON when
   running \verb|ccmake|.

\end{enumerate}

@@

The display server can present HTML forms and send data from a form to a client
when the form is submitted. The data from a form can also be saved into a
persistent storage and reloaded later. This way the forms can be used to
configure the components from the user interface instead of using CAST
configuration files.

@@

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   #ifdef FEAT_VISUALIZATION
   class COrDisplayClient: public cogx::display::CDisplayClient
   {
      CObjectRecognizer* pRecognizer;
   public:
      void createForms();
      void handleForm(const std::string& id, const std::string& partId,
            const std::map<std::string, std::string>& fields); /*override*/
      bool getFormData(const std::string& id, const std::string& partId,
            std::map<std::string, std::string>& fields); /*override*/
   };
   #endif
\end{Verbatim}

A form can be defined with standard HTML form elements but it must not be
enclosed in the \code{"<form>"} tag which is added by the Display Server.  The
"submit" button will also be added by the Display Server.  It will be placed
above the form along with the other buttons that handle form data.  If you want
the button placed in a different location, simply add another one like in the
example below:
